Curriculum and Imitation Learning for Bipedal Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
Add more figures to paper: curriculum and FSM visualizations

@@

See Table \ref{table:params} for a summary of the parameters of the TG.
These parameters are \emph{residual} in the sense that setting all of them to zero will produce the default behavior of the TG.
Examples of this default behavior can be seen in the supplemental video.
On its own, the TG can walk forward, walk in a circle, and to some extent control the length of its steps.
However, it cannot hit footstep targets with high accuracy, and it usually falls when climbing stairs.
Now that we have incorporated significant prior knowledge into the design of the TG, we turn our attention to the learning aspects of our approach.

@@

>>>>

\begin{figure}
  \includegraphics[width=0.15\textwidth]{../figures/TOE_OFF.png}
  \includegraphics[width=0.12\textwidth]{../figures/UP.png}
  \includegraphics[width=0.175\textwidth]{../figures/DOWN.png}
  \caption{\label{fig:fsm} Visualization of target joint angles for the locomotion TG.
  State TOE-OFF (left) transitions to state UP (middle) after 0.2s, which transitions to state DOWN once the robot is close to the target location.
  Finally, state DOWN transitions to state UP upon heel-strike.}
\end{figure}

@@

See Fig. \ref{fig:fsm} for a visualization of the TG's states, and
see Table \ref{table:params} for a summary of the parameters of the TG.
These parameters are \emph{residual} in the sense that setting all of them to zero will produce the default behavior of the TG.
Examples of this default behavior can be seen in the supplemental video.
On its own, the TG can walk forward, walk in a circle, and to some extent control the length of its steps.
However, it cannot hit footstep targets with high accuracy, and it usually falls when climbing stairs.
Now that we have incorporated significant prior knowledge into the design of the TG, we turn our attention to the learning aspects of our approach.

@@

\begin{figure}
  \includegraphics[width=0.48\textwidth]{../figures/2D_EASY.png}
  \includegraphics[width=0.48\textwidth]{../figures/2D_HARD.png}
  \includegraphics[width=0.48\textwidth]{../figures/3D_EASY.png}
  \includegraphics[width=0.48\textwidth]{../figures/3D_MEDIUM.png}
  \includegraphics[width=0.48\textwidth]{../figures/3D_HARD.png}
  \caption{\label{fig:curriculum} Example episodes from the various environments used in the locomotion curriculum.
  Top to bottom: 2D-Easy, 2D-Hard, 3D-Easy, 3D-Medium, and 3D-Hard.}
\end{figure}
